Self-assembly of colloid-cholesteric composites: A route to switchable optical materials

### 2013-10-18 papers/2012-sandwich/support.tex
Added results of run with E_y-field
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2198 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.95\columnwidth]{support-fig7.pdf}
\end{center}
\caption{Panels A and B as for Fig. 3, but with the disclination lines
removed for clarity. Panel C shows the situation when the field is
switched off: a residual anisotropic structure remains which reflects the
structure induced by the electric field. The electric field direction
when switched on (panel B) is into the plane of the paper.}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.95\columnwidth]{support-fig7.pdf}
\includegraphics[width=0.5\columnwidth]{support-fig7d.png}
\end{center}
\caption{Panels A and B as for Fig. 3, but with the disclination lines
removed for clarity. Panel C shows the situation when the field is
switched off: a residual anisotropic structure remains which reflects the
structure induced by the electric field. The electric field direction
when switched on (panel B) is into the plane of the paper and along z.}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.24\columnwidth]{support-fig8a.png}
\includegraphics[width=0.24\columnwidth]{support-fig8b.png}
\includegraphics[width=0.24\columnwidth]{support-fig8c.png}
\includegraphics[width=0.24\columnwidth]{support-fig8d.png}\\
\includegraphics[width=0.24\columnwidth]{support-fig8e.png}
\includegraphics[width=0.24\columnwidth]{support-fig8f.png}
\includegraphics[width=0.24\columnwidth]{support-fig8g.png}
\includegraphics[width=0.24\columnwidth]{support-fig8h.png}
\end{center}
\caption{Particle distribution and structure factor in electric fields and after switch-off:
The top images show the ordering of the particles in an electric field along the x-direction 
after a previous run which had the field along z. For clarity all disclination lines have
been removed and the view is with the field direction into the paper plane. 
The bottom row depicts results for a consecutive run with the field now 
oriented along the y-direction. In the left panels the field is on, whereas the right panels 
show the situation after switch-off. 
The structure factor data is for wave vectors $k_y, k_z \in [-3\pi/8 , 3\pi/8]$.}
\end{figure}
